### 2024-04-22 parts/correction.tex
moving two variables paragraphs

Let us now state, for the sake of completeness, the equality of $\CorrectPoly$
and $\CoveredPoly$ in the case of two indeterminates. This is relevant because
it shows that examples given in \cite{KARH77} are actually correct, even though
based on an invalid result, and it may be the case for other works based on
\cite{KARH77}. The proof is based the fact that for (non-negative) univariate
it is enough that the dominant coefficient is non-negative to be an
\kl{$\Nat$-rational polynomial}.

>>>>

The counter example of \cref{thm:counter-example} used three indeterminates,
and we will prove in \cref{sec:proof} that \cref{karh:thm} holds on polynomial
with at most two indeterminate. In particular, the examples appearing in
\cite{KARH77} are not invalidated, as they all use at most two indeterminates.
In particular, we derive the equality of $\CorrectPoly$ and $\CoveredPoly$ in
the case of two indeterminates.  The proof is based the fact that for
(non-negative) univariate it is enough that the dominant coefficient is
non-negative to be an \kl{$\Nat$-rational polynomial}.

### 2024-04-22 parts/counter.tex
appendix + proofrefs
typos
moving two variables paragraphs

\begin{remark}
    \label{n-poly-n-poly:example}
    Let $P \in \Nat[\vec{X}]$. Then, $P$
    is an \kl{$\Nat$-rational polynomial}.
\end{remark}

\begin{example}
    \label{negative-but-npoly:ex}
    Let $P \defined X^2 -2X + 2$. Then $P$
    is an \kl{$\Nat$-rational polynomial}.
\end{example}

@@

\begin{faketheorem}[{\cite[Theorem 3.3, page 4]{KARH77}}] 
    \label{karh:thm}
    Let $\Sigma$ be a finite alphabet
    and $P$ be a polynomial. The following are equivalent:
    \begin{enumerate}
        \item $P$ is an \kl{$\Nat$-rational polynomial},
        \item $P \in \CoveredPoly$.
    \end{enumerate}
\end{faketheorem}

@@

Let us now provide a counter example to \cref{karh:thm}. The counter example
will use three indeterminates, and we will prove in \cref{sec:proof} that
\cref{karh:thm} holds on polynomial with at most two indeterminate. In
particular, the examples appearing in \cite{KARH77} are not invalidated, as
they all use at most two indeterminates. Furthermore, the converse implication,
that is, that \kl{$\Nat$-rational polynomials} belong to $\CoveredPoly$ is
correct, and can even be strengthened as we will see in
\cref{corrected-version:thm}.

>>>>

\begin{lemma}
    \label{n-poly-n-poly:example}
    Let $P \in \Nat[\vec{X}]$. Then, $P$
    is an \kl{$\Nat$-rational polynomial}.
    \proofref{n-poly-n-poly:example}
\end{lemma}

\begin{example}
    \label{negative-but-npoly:ex}
    Let $P \defined X^2 -2X + 2$. Then $P$
    is an \kl{$\Nat$-rational polynomial}.
    \proofref{negative-but-npoly:ex}
\end{example}

@@

\begin{faketheorem}[{\cite[Theorem 3.3, page 4]{KARH77}}] 
    \label{karh:thm}
    Let $\Sigma$ be a finite alphabet
    and $P$ be a polynomial. Then,
    $P$ is an \kl{$\Nat$-rational polynomial}
    if and only if 
    $P \in \CoveredPoly$.
\end{faketheorem}

@@

Let us now provide a counter example to \cref{karh:thm}.
